Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-09-13 Rdocs/Plots.Rmd
finalized plot Rmd file, knitted to pdf output standardized plots

---
title: Biodegradable alternatives to plastic mesh bags conventionally used in freshwater
  macroinvertebrate analysis within the Bronx River, NYC
author: "R.E. Segui-Baez, G.A. Rueda Moreno, R. Ward, K. Schneider Paolantonio"
date: "`r Sys.Date()`"
output: word_document
bibliography: references.bib
---

```{r pre-requisite scripts, echo=FALSE}
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/stats.R") #script to analyze previously loaded data

@@

```{r setup, include=FALSE}
#knitr options----
knitr::opts_chunk$set(echo = TRUE)
#dependencies----
require(tidyverse)
require(GGally)
require(vegan)
require(ggpubr)
require(tidyverse)
require(viridisLite)
require(rlang)
require(car)
require(corrplot)
require(factoextra)

@@

    theme_bw() +
    scale_fill_viridis_d()+
    theme_rafa(base_size = 15) +
    theme(axis.text.x = element_text(angle = -15, vjust = 0.5))+
    labs(x = "material", title = "Diversity Index by Bag material", y = paste(index),
         fill = "material")
}

@@

### Tables

```{r wq table}
readxl::read_xlsx("Rfigs/summaryFigures.xlsx", sheet = 2) %>%
knitr::kable(caption = "Table 2: Water quality parameters averaged over the course of the sampling period")
```

### Plots

```{r wq plots, eval=FALSE}
#water quality dot plots----
#water quality by date on the y and site as color
wq_ts_BySite("P") +labs( title = "Phosphorous Seasonality",y = "Phosphorous (mg/L)")
wq_ts_BySite("pH")
wq_ts_BySite("NH3") +labs(y = "Ammonia (mg/L)")
wq_ts_BySite("DO") + labs(title = "Dissolved Oxygen Seasonality",
                          y = "% DO")
wq_ts_BySite("Temp") + labs(title = "Temperature Seasonality",
                            y = "Temp (°C)")
wq_ts_BySite("Cond") + labs(title = "Conductivity Seasonality", y = "Conductivity (mS)")
wq_ts_BySite("Nitrogen") + labs(y = "Nitrogen (mg/L)")
wq_ts_BySite("Flow") + labs(title = "Flow rate Seasonality",
                            x = "Date", y = "Flow (m/s)")

@@

#by material (plastic comparisons only)
ggplot(BC_ByMat_tibble[7:10,], aes(x = mat_comp, y = bc_score, fill = mat_comp)) +geom_col() +
  theme_rafa() + scale_fill_viridis_d()+
  coord_cartesian(ylim = c(0, 1)) +
  labs(title = "Community Dissimilarity between plastic and biodegradable bags", x = "Material Comparison",
       y = "Bray Curtis Dissimilarity", fill = "Comparisons")

@@

#plotting
ggplot(TC_NMDS_Scores, aes(x = NMDS1, y = NMDS2, fill = material)) +
  geom_hline(yintercept = 0, linetype = 5) + geom_vline(xintercept = 0, linetype = 5) +
  geom_point(shape = 21, size = 2.5) +
  facet_wrap(~date)+
  theme_rafa() +
  labs(title = "Non-Metric Dimensional Scaling of Community Matrices")+
  scale_fill_viridis_d()
```

>>>>

---
output:
  pdf_document: default
  html_document: default
---

```{r pre-requisite scripts, echo=FALSE, results='hide',message=FALSE,warning=FALSE}
#set knitr options----
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
#source data processor scripts----
source("Rscripts/biodiversity.R")#script to process biodiversity data
source("Rscripts/water_quality.R")#script to process water quality data
source("Rscripts/stats.R") #script to analyze previously loaded data

@@

```{r setup,echo=FALSE, results='hide',message=FALSE,warning=FALSE}
#dependencies----
require(tidyverse)
require(GGally)
require(vegan)
require(ggpubr)
require(tidyverse)
require(viridisLite)
require(rlang)
require(car)
require(corrplot)
require(factoextra)

@@

    theme_bw() +
    scale_fill_viridis_d()+
    theme_rafa(base_size = 15) +
    theme(axis.text.x = element_text(angle = -15, vjust = 0.5))+
    labs(x = "material", title = "Index by Bag material", y = paste(index),
         fill = "material")
}

@@

# Leaf Pack Project Plots

```{r wq plots, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
#water quality dot plots----
#water quality by date on the y and site as color
wq_ts_BySite("P") +labs( title = "Phosphorous Seasonality",y = "Phosphorous (mg/L)")
wq_ts_BySite("pH")
wq_ts_BySite("NH3") +labs(y = "Ammonia (mg/L)")
wq_ts_BySite("DO") + labs(title = "Dissolved Oxygen Seasonality",
                          y = "% DO")
wq_ts_BySite("Temp") + labs(title = "Temperature Seasonality",
                            y = "Temp (°C)")
wq_ts_BySite("Cond") + labs(title = "Conductivity Seasonality", y = "Conductivity (mS)")
wq_ts_BySite("Nitrogen") + labs(y = "Nitrogen (mg/L)")
wq_ts_BySite("Flow") + labs(title = "Flow rate Seasonality",
                            x = "Date", y = "Flow (m/s)")

@@

#by material (plastic comparisons only)
ggplot(BC_ByMat_tibble[7:10,], aes(x = mat_comp, y = bc_score, fill = mat_comp)) +geom_col() +
  theme_rafa() + scale_fill_viridis_d()+
  coord_cartesian(ylim = c(0, 1)) +
  labs(title = "Community Dissimilarity between \n plastic and biodegradable bags", x = "Material Comparison",
       y = "Bray Curtis Dissimilarity", fill = "Comparisons")

@@

#plotting
ggplot(TC_NMDS_Scores, aes(x = NMDS1, y = NMDS2, fill = material)) +
  geom_hline(yintercept = 0, linetype = 5) + geom_vline(xintercept = 0, linetype = 5) +
  geom_point(shape = 21, size = 2.5) +
  facet_wrap(~date)+
  theme_rafa() +
  labs(title = "Bray Curtis NMDS of Community Matrices")+
  scale_fill_viridis_d()
```
